\begin{thebibliography}{99}

\bibitem{jurafsky2023speech}
D. Jurafsky and J. H. Martin.
\textit{Speech and Language Processing}.
Draft available online, 2023.

\bibitem{manning2008ir}
C. D. Manning, P. Raghavan, and H. Schütze.
\textit{Introduction to Information Retrieval}.
Cambridge University Press, 2008.

\bibitem{salton1988term}
G. Salton and C. Buckley.
Term-weighting approaches in automatic text retrieval.
\textit{Information Processing \& Management}, 24(5):513--523, 1988.

\bibitem{cortes1995support}
C. Cortes and V. Vapnik.
Support-vector networks.
\textit{Machine Learning}, 20:273--297, 1995.

\bibitem{fan2008liblinear}
R.-E. Fan, K.-W. Chang, C.-J. Hsieh, X.-R. Wang, and C.-J. Lin.
LIBLINEAR: A library for large linear classification.
\textit{Journal of Machine Learning Research}, 9:1871--1874, 2008.

\bibitem{pang2008opinion}
B. Pang and L. Lee.
Opinion mining and sentiment analysis.
\textit{Foundations and Trends in Information Retrieval}, 2(1--2):1--135, 2008.

\bibitem{liu2012sentiment}
B. Liu.
\textit{Sentiment Analysis and Opinion Mining}.
Morgan \& Claypool Publishers, 2012.

\bibitem{robertson2009probabilistic}
S. Robertson and H. Zaragoza.
The probabilistic relevance framework: BM25 and beyond.
\textit{Foundations and Trends in Information Retrieval}, 3(4):333--389, 2009.

\bibitem{cormack2009rrf}
G. V. Cormack, C. L. A. Clarke, and S. Büttcher.
Reciprocal rank fusion outperforms Condorcet and individual rank learning methods.
In \textit{Proceedings of SIGIR}, pages 758--759, 2009.

\bibitem{johnson2019billion}
J. Johnson, M. Douze, and H. Jégou.
Billion-scale similarity search with GPUs.
\textit{IEEE Transactions on Big Data}, 7(3):535--547, 2019.

\bibitem{lewis2020rag}
P. Lewis, E. Perez, A. Piktus, F. Petroni, V. Karpukhin, and others.
Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks.
In \textit{Advances in Neural Information Processing Systems}, 2020.

\bibitem{devlin2019bert}
J. Devlin, M.-W. Chang, K. Lee, and K. Toutanova.
BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding.
In \textit{Proceedings of NAACL-HLT}, 2019.

\bibitem{conneau2020xlmr}
A. Conneau, K. Khandelwal, N. Goyal, and others.
Unsupervised Cross-lingual Representation Learning at Scale.
In \textit{Proceedings of ACL}, 2020.

\bibitem{nguyen2020phobert}
D. Q. Nguyen and A. T. Nguyen.
PhoBERT: Pre-trained language models for Vietnamese.
In \textit{Findings of EMNLP}, pages 1037--1042, 2020.

\bibitem{reimers2019sentencebert}
N. Reimers and I. Gurevych.
Sentence-BERT: Sentence Embeddings using Siamese BERT-Networks.
In \textit{Proceedings of EMNLP-IJCNLP}, 2019.

\bibitem{wang2022e5}
L. Wang, N. Yang, X. Huang, B. Jiao, L. Yang, D. Jiang, R. Majumder, and F. Wei.
Text Embeddings by Weakly-Supervised Contrastive Pre-training.
\textit{arXiv preprint arXiv:2212.03533}, 2022.

\bibitem{nogueira2019passage}
R. Nogueira and K. Cho.
Passage Re-ranking with BERT.
\textit{arXiv preprint arXiv:1901.04085}, 2019.

\bibitem{vaswani2017attention}
A. Vaswani, N. Shazeer, N. Parmar, and others.
Attention Is All You Need.
In \textit{Advances in Neural Information Processing Systems}, 2017.

\bibitem{pedregosa2011scikit}
F. Pedregosa, G. Varoquaux, A. Gramfort, and others.
Scikit-learn: Machine Learning in Python.
\textit{Journal of Machine Learning Research}, 12:2825--2830, 2011.

\bibitem{khattab2020colbert}
O. Khattab and M. Zaharia.
ColBERT: Efficient and Effective Passage Search via Contextualized Late Interaction over BERT.
In \textit{Proceedings of SIGIR}, 2020.

\bibitem{karpukhin2020dense}
V. Karpukhin, B. Oğuz, S. Min, P. Lewis, L. Wu, S. Edunov, D. Chen, and W.-t. Yih.
Dense Passage Retrieval for Open-Domain Question Answering.
In \textit{Proceedings of EMNLP}, 2020.

\bibitem{pontiki2014semeval}
M. Pontiki, D. Galanis, J. Pavlopoulos, H. Papageorgiou, I. Androutsopoulos, and S. Manandhar.
SemEval-2014 Task 4: Aspect Based Sentiment Analysis.
In \textit{Proceedings of the 8th International Workshop on Semantic Evaluation}, 2014.

\bibitem{fastapi}
S. Ramirez.
FastAPI Documentation.
\url{https://fastapi.tiangolo.com/}, 2018.

\end{thebibliography}

